---
output:
  html_document:
    fig_width: 3
  pdf_document: default
  word_document: default
---
  
  
<!-- This is the starting R code chunk that forms the pie charts -->
```{r, echo=FALSE, results = 'hide', message = FALSE, warnings = FALSE}
#This area creates the plots and sets up other objects to be inserted into the RMarkdown code later on.

#---#
#The overall layout and objects sizes are determined by these variables.
image_width <- 200
fontSize <- 24
bar_plot_width <- 400
donut_plot_width <- 300
donut_plot_height <- 300
text_description_width <- 90
column_1_pixels_from_left <- 0
column_2_pixels_from_left <- 300
column_3_pixels_from_left <- 400
column_4_pixels_from_left <- 700

row_1_pixels_from_top <- 200
row_2_pixels_from_top <- 500
row_3_pixels_from_top <- 800

sample_number_for_text <- '1,350'
#---#


#----------#This section creates the plots that will later be referenced in the Markdown/HTML code.
df <- data.frame(
  group = c("Yes", "No"),
  value = c(25, 75)
)

suppressWarnings(  library(ggplot2)   ) #Load library ggplot and suppress any warnings that pop up.
#I had difficulty suppressing them purely with setting warnings = False
#at the start of the RMarkdown chunk.


# Sample Barplot
bp <- ggplot(df, aes(x="", y=value, fill=group)) +
  geom_bar(width = .35, stat = "identity", fill = c('red','orange'))

bp <- bp + labs(x="", y="")  #This removes the 'x' and 'value' labels for the x and y axes respectively.

pie <- bp + #geom_text(aes(label = '14%'), vjust = "inward", hjust = "inward") +
  coord_polar("y", start=0*pi/(180)) +  #This changes the barplot into a donut plot.
  annotate("text", x = 0, y = 0, label = "25%", size = 10, col = 'orange')


pie <- pie + theme(panel.background = ggplot2::element_blank(),
                   axis.text.x = ggplot2::element_blank(),  #This will get rid of the x-axis labels.
                   axis.ticks=element_blank())  #This will get rid of the single x-axis tick.
#----------#



```


<!-- This is the start of the Markdown/HTML section of the file. -->

<!-- This is the start of Row #1. -->
<div style="position: absolute; top: `r row_1_pixels_from_top`px;">

  <span style="padding: 10px; position: absolute; left: `r column_1_pixels_from_left`px; 
                top: 100px; width: `r donut_plot_width`px; height: `r donut_plot_height`px;">
```{r echo=FALSE}
    pie 
```       
  </span>
  
  <span style = "position: absolute; left: `r column_2_pixels_from_left`px; top: 275px; 
                width: `r text_description_width`px; vertical-align: middle; ">  
      There were a sample of <b> `r sample_number_for_text` </b> GP Out of Hours in 2018/19.
  </span>
  
  <span style = "padding: 10px; position: absolute; left: `r column_3_pixels_from_left`px; 
               top: 100px; width: `r donut_plot_width`px; height: `r donut_plot_height`px;">
```{r echo=FALSE}
    pie
```       
  </span>
  
  <span style = "position: absolute; left: `r column_4_pixels_from_left`px; top: 275px; 
                width: `r text_description_width`px; vertical-align: middle; ">  
      There were a sample of <b> `r sample_number_for_text` </b> GP Out of Hours in 2018/19.
  </span>
  
</div>


<!-- This is the start of Row #2. -->
<div style="position: absolute; top: `r row_2_pixels_from_top`px;">

  <span style="padding: 10px; position: absolute; left: `r column_1_pixels_from_left`px; 
                top: 100px; width: `r donut_plot_width`px; height: 300px;">
                <!--# out.height="200px", -->
```{r echo=FALSE} 
    pie
```       
  </span>
  
  <span style = "position: absolute; left: `r column_2_pixels_from_left`px; top: 275px; 
                width: `r text_description_width`px; vertical-align: middle; ">  
      There were a sample of <b> `r sample_number_for_text` </b> GP Out of Hours in 2018/19.
  </span>
  
  <span style = "padding: 10px; position: absolute; left: `r column_3_pixels_from_left`px; 
  top: 100px; width: `r donut_plot_width`px;">
```{r echo=FALSE}
    pie
```       
  </span>
  
  <span style = "position: absolute; left: `r column_4_pixels_from_left`px; top: 275px; 
                width: `r text_description_width`px; vertical-align: middle; ">  
      There were a sample of <b> `r sample_number_for_text` </b> GP Out of Hours in 2018/19.
  </span>
  
</div>



<!-- This is the start of Row #2. -->
<div style="position: absolute; top: `r row_3_pixels_from_top`px;">

  <span style="padding: 10px; position: absolute; left: `r column_1_pixels_from_left`px; 
                top: 100px; width: `r donut_plot_width`px;">
```{r  echo=FALSE}
    pie 
```       
  </span>
  
  <span style = "position: absolute; left: `r column_2_pixels_from_left`px; top: 275px; 
                width: `r text_description_width`px; vertical-align: middle; ">  
      There were a sample of <b> `r sample_number_for_text` </b> GP Out of Hours in 2018/19.
  </span>
  
  <span style = "padding: 10px; position: absolute; left: `r column_3_pixels_from_left`px; 
  top: 100px; width: `r donut_plot_width`px;">
```{r echo=FALSE}
    pie
```       
  </span>
  
  <span style = "position: absolute; left: `r column_4_pixels_from_left`px; top: 275px; 
                width: `r text_description_width`px; vertical-align: middle; ">  
      There were a sample of <b> `r sample_number_for_text` </b> GP Out of Hours in 2018/19.
  </span>
  
</div>








